---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# who-data


[![Build Status](https://travis-ci.org/ATFutures/who.svg)](https://travis-ci.org/ATFutures/who) 
[![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)

Data for [`who` repo](https://github.com/ATFutures/who).

# worldpop download and pre-processing (does not need to be run)

Data must be manually downloaded from [worldpop](http://www.worldpop.org.uk/).
See `?worldpop_files (type = "zip")` for list of which files need to be
obtained. These should be in the relevant `<city>/popdens` directories (where
`<city>` is "accra" or "kathmandu").  Then upload to the release
`v0.0.1-worldpop-zip-gha-npl` with
```{r, eval = FALSE}
library (whodata)
upload_worldpop_zipfiles ()
```

These should never be needed again, but can easily be downloaded from the repo
with
```{r, eval = FALSE}
download_worldpop_zipfiles ()
```

These files can then be converted to local `.tif` files with
```{r, eval = FALSE}
crop_worldpop_tif (city = "accra")
crop_worldpop_tif (city = "kathmandu")
```
And then uploaded via piggyback to corresponding release
`v0.0.2-worldpop-tif-gha-npl` with
```{r, eval = FALSE}
upload_worldpop_tiffiles ()
```
