---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# who-data


[![Build Status](https://travis-ci.org/ATFutures/who-data.svg)](https://travis-ci.org/ATFutures/who-data) 
[![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)

Data for [`who` repo](https://github.com/ATFutures/who). To obtain local copes
of all data, simply clone this repo, then run the following in the main repo
directory:
```{r, eval = FALSE}
devtools::load_all (".", export_all = FALSE)
download_who_data ()
```
That should be all that is required for to generate flow layers for each city
via the [`flowlayers` repo](https:github.com/ATFutures/flowlayers).


# Population density download and pre-processing

(None of this should need to be run; it is code used to generate the initial
files.)

## worldpop (Accra and Kathmandu)

Data must be manually downloaded from [worldpop](http://www.worldpop.org.uk/).
See `?worldpop_files (type = "zip")` for list of which files need to be
obtained. These should be in the relevant `<city>/popdens` directories (where
`<city>` is "accra" or "kathmandu").  Then upload to the release
`v0.0.1-worldpop-zip-gha-npl` with
```{r, eval = FALSE}
library (whodata)
upload_worldpop_zipfiles ()
```

These should never be needed again, but can easily be downloaded from the repo
with
```{r, eval = FALSE}
download_worldpop_zipfiles ()
```

These files can then be converted to local `.tif` files with
```{r, eval = FALSE}
crop_worldpop_tif (city = "accra")
crop_worldpop_tif (city = "kathmandu")
```
And then uploaded via piggyback to corresponding release
`v0.0.2-worldpop-tif-gha-npl` with
```{r, eval = FALSE}
upload_worldpop_tiffiles ()
```

## Bristol

There are no worldpop data for Europe, but the EC Joint Research Centre Data
Catalogue offers 250m resolution global population density `tif` files.  The
main JRCDC page describing the [relevant
file](http://data.jrc.ec.europa.eu/dataset/jrc-ghsl-ghs_pop_gpw4_globe_r2015a)
leads leading to the download of
`GHS_POP_GPW42015_GLOBE_R2015A_54009_250_v1_0.zip`, which is 1GB, and is not
archived in this repo. This file can then be processed with
```{r, eval = FALSE}
crop_global_tif (city = "Bristol")
```

# Street network up- and down-load

```{r, eval = FALSE}
library (sf) # pre-load required
cities <- who_cities () # accra, kathmandu, bristol
junk <- lapply (cities, function (i) get_who_streets (city = i))
junk <- lapply (cities, function (i) get_who_buildings (city = i))
junk <- lapply (cities, function (i) get_who_busstops (city = i))
```
Then upload to repo with
```{r, eval = FALSE}
upload_osm ()
```
and download with
```{r, eval = FALSE}
download_osm ()
```

# Population densities matched to street network nodes

This is done via the [`popdens` package](https://github.com/ATFutures/popdens),
using the single `pop2point` function. Simply
```{r, eval = FALSE}
popdens::pop2point (city = "kathmandu")
popdens::pop2point (city = "accra")
whodata::upload_popdens_nodes ()
```
